A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Minor re-ordering of words

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is larger than
the incumbent.  \Linerangeref{CalcBound}{PruneSearch} prune the search when a
calculated upper bound is not large enough to unseat the incumbent.

>>>>

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is large enough
to unseat the incumbent.  \Linerangeref{CalcBound}{PruneSearch} prune the
search when a calculated upper bound is not larger than the incumbent.
